### 2021-07-11 docs/manuscript/manuscript.tex
Rephrase text

However, as our model was less stringent and allowed the morphogen input to
interact with any gene, we found a more significant number of possible topologies with the
same striped phenotype and a diverse combination of diffusion and degradation
parameters~(\nameref{S7_Fig}). For example, in a single input model, the I4-FFL could
not produce a stripe of gene expression~\cite{munteanu_2014}, whereas, in our
experimental setup, 20.17\% of the topologies presented this motif as a
subgraph~(\nameref{S1_Table}).

Although it has been experimentally demonstrated that the Incoherent Feed-Forward
Loop type 2 (I2-FFL) can generate a striped gene expression
pattern~\cite{Schaerli2014, Basu2005}, in our study, this motif was present in
only 10.92\% of the topologies. This fact may be because evolutionary algorithms
can not always find global minima but local minima or their surroundings. However,
it is also possible that the I2-FFL motif is not as robust as other motifs and
therefore be less represented.

We also found topologies with a similar topology to that of the “opposing
gradients” reported by Schaerli et al.~\cite{Schaerli2018,Schaerli2014}.
Although the “opposing gradients” mechanism requires the constitutive expression
of two of the genes in the GRN, and our model does not take constitutive
expression into account, we realized that the GRNs that presented the “opposing
gradients” topology, had also commonly positive auto-regulation interactions on
these two nodes, supplying in this way the lack of constitutive
expression as found in previous studies~\cite{munteanu_2014}.

@@

Although GRNs that produce a band of gene expression with only two nodes have
been described (e.g., the I-zero motif~\cite{Schaerli2014}), this is to our
knowledge the first time a GRN with a topology such as that of topology
nine~(Fig \ref{fig:topol9})
and its expression mechanism is reported, increasing our knowledge of the
genotype-phenotype map in this kind of system. It would be very interesting
to confirm experimentally the ability of this topology to generate the described
pattern and it would be interesting to study its feasibility and possible
implementation in synthetic gene regulatory networks.

This work provides a catalog of GRNs that can be extended in future computational
and theoretical analysis and provides a foundation to design and build synthetic
regulatory networks or identify new ones existing in nature.

>>>>

However, as our model was less stringent and allowed the morphogen input to
interact with any gene, we found a significantly larger number of pattern-forming
topologies, which can operate under disparate combinations of diffusion and degradation
parameters~(\nameref{S7_Fig}). For example, in a single input GRN model, the I4-FFL
has not been found capable of generating a striped gene expression
pattern~\cite{munteanu_2014}, whereas, in our experimental setup, 20.17\% of
the topologies were found  to implement such a regulatory motif~(\nameref{S1_Table}).

Although recent experimental evidence highlights the importance of the Incoherent
Feed-Forward Loop type 2 (I2-FFL) for generating a striped gene expression
pattern~\cite{Schaerli2014, Basu2005}, it is intriguing to find that such motif is
underrepresented in our study, with only 10.92\% of the topologies implementing
such regulatory mechanism. This might be due to the difficulty to find optimal
solutions when probing the design space of multi-input GRNs, which are likely to
contain multiple locally optimal solutions. In addition, it is important to mention
here that the application of a MCMC-like algorithm as a search space strategy for
such complex tasks cannot be expected to allow for extensive exploration of the
design space of GRNs nor for the accessibility of every single locally optimal
solution. However, it is also possible that the I2-FFL motif is not as robust as
other motifs and therefore be less represented.

We also found topologies with a similar topology to that of the “opposing
gradients” reported by Schaerli et al.~\cite{Schaerli2018,Schaerli2014}.
Although the “opposing gradients” mechanism requires the constitutive expression
of two of the genes in the GRN, and our model does not take constitutive
expression into account, we observed that the GRNs that implement the “opposing
gradients” mechanism also tend to implement auto-regulation interactions on
these two nodes, bypassing in this way the lack of constitutive
expression as found in previous studies~\cite{munteanu_2014}.

@@

Although GRNs that produce a band of gene expression with only two nodes have
been described (e.g., the I-zero motif~\cite{Schaerli2014}), this is to our
knowledge the first time that a novel GRN topology such as number
9~(Fig \ref{fig:topol9}) has been reported, which adds considerably to existing
knowledge on the genotype-phenotype mapping problems studied in the
context of developmental pattern formation. It would be interesting to assess
experimentally the ability of this particular topology to generate striped gene
expression patterns, as well as to assess its robustness in the face of mutational
changes and noisy morphogen input profiles.

Overall, we believe our work provides a set of enticing hypotheses on GRN designs,
represented as a large catalog of distinct GRN topologies that could provide
valuable information as starting points for future computational and theoretical
analysis of the genotype-phenotype map, as well as for experimental validation and
future discovery of potentially interesting GRN designs.
